Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-02-19 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix typos suggested by Andy...

The above arguments could be summarized and illustrated using
Fig.~\ref{fignoname}. An additional perspective on the physical
interpretation of the theorem is in the appendix.

@@

Meyer's insight and the main assumption in his proof that using the
field of rationals nullifies the Kochen-Specker theorem.  In other
words, Meyer exclusively attributes finite-precision errors to the
description of the states defined in a general Hilbert space. The
response of Mermin, argues against Meyer's interpretation but accepts
his framework. More generally, there have been responses that argue
that the effect of finite-precision measurements on the Kochen-Specker
theorem requires a different approach altogether (see for example Ax
and Kochen's communication cited by Cabello~\cite{Cabello2002}). Our
approach is agnostic about attributing elements of reality to the
state function (as Meyer did). We simply attribute lack of certainty
to the uncertain results obtained through the use of a measuring
instrument. Thus, the parameter~$\delta$ in our framework reflects
insufficient knowledge of the experimenter, which could be due to a
variety of reasons related to imperfections of devices. For example, a
typical question that an experimenter may not be able to answer
accurately would be ``did an electron land in the left half or the
right half of the screen?''  There are cases in which the electron
would land too close to the middle of the screen for the experimenter
to be able to determine with certainty that it was left or right of
the center. We simply record this imprecision in the probability we
assign to events, and use the axioms of probability theory to argue
that a sharp transition occurs when the imprecision reaches a certain
value.

>>>>

We can summarize and illustrate the above arguments using
Fig.~\ref{fignoname}. An additional perspective on the physical
interpretation of the theorem is in the appendix.

@@

This is Meyer's great insight and the main assumption in his proof that using the
field of rationals nullifies the Kochen-Specker theorem.  In other
words, Meyer exclusively attributes finite-precision errors to the
description of the states defined in a general Hilbert space. The
response of Mermin, argues against Meyer's interpretation but accepts
his framework. More generally, there have been responses that argue
that the effect of finite-precision measurements on the Kochen-Specker
theorem requires a different approach altogether (see for example Ax
and Kochen's communication cited by Cabello~\cite{Cabello2002}). Our
approach is agnostic about attributing elements of reality to the
state function (as Meyer did). We simply attribute lack of certainty
to the uncertain results obtained through the use of a measuring
instrument. Thus, the parameter~$\delta$ in our framework reflects
insufficient knowledge of the experimenter, which could be due to a
variety of reasons related to imperfections of devices. For example, a
typical question that an experimenter may not be able to answer
accurately would be ``did an electron land in the left half or the
right half of the screen?''  There are cases in which the electron
would land too close to the middle of the screen for the experimenter
to be able to determine with certainty that it was left or right of
the center. We simply record this imprecision in the probability we
assign to events, and use the axioms of probability theory to argue
that a sharp transition occurs when the imprecision reaches a certain
value.
